Introduction to\\ Swedish Civil Contingencies Agency (MSB) methodological support for introducing \ac{isms}.

### 2017-04-04 msbframework/msbintro/msbintro.tex
Fixed spelling errors, and removed the plural form of the acronyms
Signed-off-by: LENFRA <lennart.franked@miun.se>

\title[Intro MSB]{%
  Introduction to\\
  Swedish Civil Contingencies Agency (MSB) methodological support for introducing \acp{isms}.
}
\author{Carina Bengtsson, Daniel Bosk and Lennart Franked\footnote{%
  Detta verk är tillgängliggjort under licensen Creative Commons 
  Erkännande-DelaLika 2.5 Sverige (CC BY-SA 2.5 SE).
	För att se en sammanfattning och kopia av licenstexten besök URL 
	\url{http://creativecommons.org/licenses/by-sa/2.5/se/}.
}}
\institute[MIUN IST]{%
  Department of Informationsystem and Technologies (IST),\\
  Mid Sweden University, Sundsvall.

@@

\begin{frame}{Information Security Management System (ISMS)}
  \begin{itemize}
    \item Should be integrated with the other management systems!
    \item Refers to how to regulate the work with information security.
    \item Also how to regulate work routines, methods \dots
    \item Governance documents have an important role to play in \acp{isms}\@.
  \end{itemize}
\end{frame}

\begin{frame}{Apply \acp{isms}}
  Not only establish, but also
  \begin{itemize}
    \item implement,
    \item pursue,
    \item monitor,
    \item audit,
    \item maintain and improve
  \end{itemize}
\end{frame}

@@

\begin{frame}{Purpose with \acp{isms}}
  \begin{figure}
    \includegraphics[width=\textwidth]{infosak-pdca.png}
    \caption{To convert requirements to an active protection.}
  \end{figure}
\end{frame}

\begin{frame}{ISO 27001}
  \begin{itemize}
    \item MSB's methodological support, describes how to build an \acp{isms},
      based on ISO 27001.

@@

\begin{frame}{Project planning}
  \begin{itemize}
    \item MSB recommends that an \acp{isms} should start in project form and
      then go over to become a process.
  \end{itemize}
  \begin{figure}
    \includegraphics[height=0.5\textheight]{lis.png}
    \caption{Establish and implement an \acp{isms}.}
  \end{figure}
\end{frame}

\begin{frame}{Project plan}
  \begin{itemize}
    \item The foundation of the project.
    \item Defines the extent of the \acp{isms}\@.
    \item An agreement that is good for both the project leader and the
      management.
    \item Can contain:
      \begin{itemize}
        \item Background and need,
        \item purpose,
        \item goal,
        \item extent och demarcation,
        \item connections and contact surfaces,
        \item time plan, and
        \item budget.
      \end{itemize}
  \end{itemize}
\end{frame}

@@

\begin{frame}{A short checklist}
  \begin{itemize}
    \item Have the management made a decision to implement \acp{isms}?
    \item Have the management appointed someone to coordinate the organisations
      work with information security?
    \item Have the management ensured that there is a strategy to communicate
      the work with \acp{isms} internally?
    \item Have the management made a decision regarding the budget and
      resources?
  \end{itemize}
\end{frame}

@@

\begin{frame}{MSB:s suggestion on a classification model}
  \begin{figure}
    \includegraphics[height=0.7\textheight]{msb-klassificering.png}
    \caption{MSB:s suggestion on a classification model.}
  \end{figure}
\end{frame}

>>>>

\title[Intro MSB]{%
  Introduction to\\
  Swedish Civil Contingencies Agency (MSB) methodological support for introducing \ac{isms}.
}
\author{Carina Bengtsson, Daniel Bosk and Lennart Franked\footnote{%
  Detta verk är tillgängliggjort under licensen Creative Commons 
  Erkännande-DelaLika 2.5 Sverige (CC BY-SA 2.5 SE).
	För att se en sammanfattning och kopia av licenstexten besök URL 
	\url{http://creativecommons.org/licenses/by-sa/2.5/se/}.
}}
\institute[MIUN IST]{%
  Department of Informationsystem and Technologies (IST),\\
  Mid Sweden University, Sundsvall.

@@

\begin{frame}{Information Security Management System (ISMS)}
  \begin{itemize}
    \item Should be integrated with the other management systems!
    \item Refers to how to regulate the work with information security.
    \item Also how to regulate work routines, methods \dots
    \item Governance documents have an important role to play in \ac{isms}\@.
  \end{itemize}
\end{frame}

\begin{frame}{Apply \ac{isms}}
  Not only establish, but also
  \begin{itemize}
    \item implement,
    \item pursue,
    \item monitor,
    \item audit,
    \item maintain and improve
  \end{itemize}
\end{frame}

@@

\begin{frame}{Purpose with \ac{isms}}
  \begin{figure}
    \includegraphics[width=\textwidth]{infosak-pdca.png}
    \caption{To convert requirements to an active protection.}
  \end{figure}
\end{frame}

\begin{frame}{ISO 27001}
  \begin{itemize}
    \item MSB's methodological support, describes how to build an \ac{isms},
      based on ISO 27001.

@@

\begin{frame}{Project planning}
  \begin{itemize}
    \item MSB recommends that an \ac{isms} should start in project form and
      then go over to become a process.
  \end{itemize}
  \begin{figure}
    \includegraphics[height=0.5\textheight]{lis.png}
    \caption{Establish and implement an \ac{isms}.}
  \end{figure}
\end{frame}

\begin{frame}{Project plan}
  \begin{itemize}
    \item The foundation of the project.
    \item Defines the extent of the \ac{isms}\@.
    \item An agreement that is good for both the project leader and the
      management.
    \item Can contain:
      \begin{itemize}
        \item Background and need,
        \item purpose,
        \item goal,
        \item extent och demarcation,
        \item connections and contact surfaces,
        \item time plan, and
        \item budget.
      \end{itemize}
  \end{itemize}
\end{frame}

@@

\begin{frame}{A short checklist}
  \begin{itemize}
    \item Have the management made a decision to implement \ac{isms}?
    \item Have the management appointed someone to coordinate the organisations
      work with information security?
    \item Have the management ensured that there is a strategy to communicate
      the work with \ac{isms} internally?
    \item Have the management made a decision regarding the budget and
      resources?
  \end{itemize}
\end{frame}

@@

\begin{frame}{MSB:s suggestion on a classification model}
  \begin{figure}
    \includegraphics[height=0.7\textheight]{msb-klassificering.png}
    \caption{MSB:s suggestion on a classification model with levels: Severe, Considerable,
      Moderate, Negligible.}
  \end{figure}
\end{frame}
